Space is the Place: Effects of Continuous Spatial Structure on Analysis of Population Genetic Data

### 2019-11-21 ms/spaceness.tex
adding hexbin qqplots as supp fig

Figure \ref{fig:gwas}D shows quantile-quantile plots for a subset of simulations that show the degree of genome-wide inflation of test statistics in PC-corrected GWAS across all simulations and environmental distributions. 
For clinal environments, $-\log_{10}(p)$ values are most inflated when neighborhood sizes are large, consistent with the pattern observed in the count of significant associations after PC regression. In contrast corner and patchy environments cause the greatest inflation in $-\log_{10}(p)$ at neighborhood sizes less than 100, which likely reflects the inability of PCA to account for fine-scale structure caused by very limited dispersal. Finally, we observed that PC regression appears to overfit to some degree for all phenotype distributions, visible in Figure \ref{fig:gwas}D as points falling below the 1:1 line.

@@

>>>>

Figure \ref{fig:gwas}D shows quantile-quantile plots for a subset of simulations that show the degree of genome-wide inflation of test statistics in PC-corrected GWAS across all simulations and environmental distributions. 
An alternate visualization is also included in figure \ref{fig:qqplot_hexbins}.
For clinal environments, $-\log_{10}(p)$ values are most inflated when neighborhood sizes are large, consistent with the pattern observed in the count of significant associations after PC regression. In contrast corner and patchy environments cause the greatest inflation in $-\log_{10}(p)$ at neighborhood sizes less than 100, which likely reflects the inability of PCA to account for fine-scale structure caused by very limited dispersal. Finally, we observed that PC regression appears to overfit to some degree for all phenotype distributions, visible in Figure \ref{fig:gwas}D as points falling below the 1:1 line.

@@

\begin{figure*}[p]
\centering
\includegraphics[width=0.8\textwidth]{figures/qqplots_hexbin.pdf}
\caption{Quantile-quantile plots showing observed and expected $-log10(p)$ for PC-corrected GWAS run on simulations with varying neighborhood sizes and environmental distributions. Hexagonal bins are colored by the average neighborhood size of simulations with points falling in a given region of quantile-quantile space. Qqplots for a subset of these simulations are shown as lines in Figure \ref{fig:gwas}D.} 
\label{fig:qqplot_hexbins}
\end{figure*}
\FloatBarrier
